Redundant calibration as a complex optimization problem

### 2017-01-24 paper.tex
improved figures

\begin{figure*}
\centering
\subfigure[Hexagonal layout]
{\includegraphics[width=0.33\textwidth]{./HEX_lay.pdf}\label{fig:HEX_lay}}
\subfigure[Square layout]
{\includegraphics[width=0.33\textwidth]{./SQR_lay.pdf}\label{fig:SQR_lay}}
\subfigure[Regular east-west layout]
{\includegraphics[width=0.33\textwidth]{./REG_lay.pdf}\label{fig:REG_lay}}

>>>>

\begin{figure*}
\centering
\subfigure[Hexagonal layout]
{\includegraphics[width=0.32\textwidth]{./HEX_lay.pdf}\label{fig:HEX_lay}}
\subfigure[Square layout]
{\includegraphics[width=0.32\textwidth]{./SQR_lay.pdf}\label{fig:SQR_lay}}
\subfigure[Regular east-west layout]
{\includegraphics[width=0.32\textwidth]{./REG_lay.pdf}\label{fig:REG_lay}}
